---
title: "Introduction to R Markdown"
author: "Adrian Darian"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
---

This assignment will introduce you to the `R Markdown` coding language.  Moreover, this `R Markdown` file (note the *.rmd extension) is a setting called "literate programming" where a user can alternate between regular typing---enhanced with markdown---and computer code (`R` or `Python`).  For reference, here is RStudio's own cheat sheet for R Markdown via the "Cheat Sheets" menu on the left.

---

Type your full name in the `author` field above.  State your major (including emphasis if applicable) and list your classes for this semester---course number and course name---below as an ***ordered-list***, from the one you think will be the most difficult to the least difficult.

Major: **Computer Science and Engineering**

1. Math 32 Probability and Statistics
2. CSE 185 Computer Vision
3. CSE 162 Mobile Computing
4. CSE 120 Software Engineering

---

Why are you enrolled in Math 32? What are you hoping to learn and gain? (Please supply an answer that is more in-depth than "This course fulfills my statistics requirement".)

I really want to learn more about R, because I have messed with it before but have a hard time choosing it over Python or JavaScript when I have a task to do some data analysis.

---

In 2-3 sentences, type a science fact that you find fascinating into the code block.  Set the parameters `echo = TRUE` and `eval = FALSE` so that RStudio does not treat the following as R code.

```{r, echo = TRUE, eval = TRUE}
# The black hole that is at the center of our galaxy has a friend that spins in circles with and scientists are trying to get video proof of this and not just photos

```

---

Spend about 5 to 10 minutes typing out your answer to "What are you hopes and goals?" as a ***bullet-point list***.  Do not worry about grammar; just type fast.

* Graduate College with my degree in hand
* Complete all migrations of servers in the CatCard office to make it easier for new developers
* Finish my personal website
* Get a job where I can make an impact building some software to help change the world
* Work on side projects 
* Travel the world, visiting different places and taking my work on the road with me
* Renovate my own apartment and make it all custom

---

Spend about 5 minutes typing out your answer to "What are your fears and obstacles?" into the code block.  Set the parameters `echo = FALSE` so that you do not show this part to your teachers and `eval = FALSE` so that RStudio does not treat the following as R code.

```{r, echo = FALSE, eval = FALSE}
# The only fears I have are not graduating, not getting a job, and then not being able to enjoy life.

```

---

For this semester, instructor Derek wants to assemble a class playlist of popular music.  What is a good, lively song to add to a class playlist?  Place the song title between asterisks to *italicize* the song title and place the artist between two-pairs of asterisks so that the artist name appears in **boldface**.  (Beyond profanity, please avoid offensive content.)

*Faster Car* - **Loving Caliber**

---

To submit this homework,

* Save your work in the "Introduction_-_your name.rmd" convention
* `knit` the code.  You should be able to see the HTML file in the Files pane (bottom right area here in RStudio Cloud)
* Go to the Files pane (bottom right area here in RStudio Cloud), click the "More" button, check the box by the HTML file, then "Export"
* upload the HTML file back into our CatCourses page
